---
title: "Airbnb Europe Cities"
author: "Meiry Fernanda Diniz"
date: "21/03/2024"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

# Airbnb Price For Europe Cities

**Airbnb Price For Europe Cities** is a Capstone Project that was developed to demonstrate the skills I acquired on the [Inco Academy's](https://incoacademy.ie/) Data Analytics course.

This analysis was developed to help a fictitious client (a couple) to decide which would be the best city in Europe to purchase a rental property. In this case, my client informed me which were the five cities they were more interest in and with this information I developed the analysis.

Visit the live version of the project: [**Airbnb Price For Europe Cities**](https://docs.google.com/presentation/d/1s-5Ag5RQlRqq2wdLGUBAG_k1hN-FihLLLp62k4eZNXU/edit?usp=sharing)

------------------------------------------------------------------------

> ## Contents

-   [PREPARING DATA](#preparing-data)
-   [PROCESSING DATA](#processing-data)
-   [ANALYSING DATA](#analysing-data)
-   [SHARING DATA](#sharing-data)
-   [TOOLS](#tools)
-   [RESOURCE](#resource)
-   [CREDITS](#credits)

------------------------------------------------------------------------

> ## Preparing Data {#preparing-data}

The dataset used to develop this analysis was imported from [Kaggle](https://www.kaggle.com/).

------------------------------------------------------------------------

> ## Processing Data {#processing-data}

[Google Sheets](https://docs.google.com/spreadsheets/create) was used to process (clean) data. `Trim whitespace`, `filter` and `conditional formating` were used to find and eliminate any errors and inaccuracies that could get in the way of results.

[Posit Cloud](https://posit.cloud/) was also used to processing data to be analysed using R.

-   **Code:**

```{r}
library(readr)
airbnb_europe_cities <- read_csv("airbnb_europe_cities.csv",
                          show_col_types = FALSE)
airbnb_selected_data <- airbnb_europe_cities %>% 
  mutate(day = ifelse(weekends, "weekend", "weekday"),
         daily_price = price / 2) %>% 
  select(city, day, daily_price, room_type, person_capacity,
         quant_bedrooms, city_center_dist_km, metro_dist_km) %>% 
  filter(room_type == 'Entire home/apt' & city %in% c('Amsterdam',
         'Barcelona','Lisbon', 'London', 'Paris')) %>% 
  group_by(city, day) %>% 
  arrange(city, day, desc(daily_price))

(airbnb_selected_data) 

```

-   **Expected Outcome:**

    -   Create new columns to have prices returned by weekday and weekend, and also have rent daily prices per person returned;

    -   Have just columns that need to be shown selected;

    -   Filter the dataset to have only data that matches the clients' request returned;

    -   Have daily price returned in descending order, and group this information by city and day.

------------------------------------------------------------------------

> ## Analysing Data {#analysing-data}

[Posit Cloud](https://posit.cloud/) was used to analyse data using R.

-   **Code:**

```{r}
airbnb_avg_price <- airbnb_selected_data %>%
  group_by(city, day) %>%
  summarize(avg_price = mean(daily_price), .groups = "drop") %>%
  arrange(desc(avg_price))

knitr::kable(airbnb_avg_price)
```

-   **Expected Outcome:**

    -   Have the average daily rental price per person returned for each city in the dataset.

[Tableau](https://public.tableau.com/) was also used to create charts to analyse data and better understand its patterns.

[Click here](https://public.tableau.com/views/AirbnbEuropeCities/Sheet1?:language=en-US&:sid=&:display_count=n&:origin=viz_share_link) to see the project on Tableau.

------------------------------------------------------------------------

> ## Sharing Data {#sharing-data}

[Google Slides](https://www.google.com/slides/about/) was used to create the presentation for this project.

Visit the live version of the project: [**Airbnb Price For Europe Cities**](https://docs.google.com/presentation/d/1s-5Ag5RQlRqq2wdLGUBAG_k1hN-FihLLLp62k4eZNXU/edit?usp=sharing)

------------------------------------------------------------------------

> ## Tools {#tools}

-   [Kaggle](https://www.kaggle.com/);
-   [Google Sheets](https://docs.google.com/spreadsheets/create);
-   [Google Slides](https://www.google.com/slides/about/);
-   [Posit Cloud](https://posit.cloud/);
-   [Tableau](https://public.tableau.com/).

------------------------------------------------------------------------

> ## Resource {#resource}

In addition to the course content I used [Stack Overflow](http://stackoverflow.com) to do research to develop my analysis.

------------------------------------------------------------------------

> ## Credits {#credits}

A public dataset from [Kaggle](https://www.kaggle.com/) was used to develop this analysis.

[Click here](https://www.kaggle.com/datasets/cahyaalkahfi/airbnb-european-cities-join) to see the original dataset.

[Click here](https://docs.google.com/spreadsheets/d/1y2_6Rk03bTh8WOns625Qk70UfrxcSI6SQgE7k8yNVoI/edit#gid=0) to see the processed dataset.
